Machine-learned embedded atom method

### 2019-10-18 doc/papers/ml-eam/manuscript.tex
The ML-EAM manuscript is updated. The first version is finally finished.

@@

The melting points $T_{m}$ of bcc Mo and fcc Ni were measured with the 
solid-liquid coexistence approach. For fcc Ni, $30 \times 10 \times 10$ 
supercells were used and for bcc the supercells were $30 \times 15 \times 15$. 
The time step was set to 1 fs. The simulation for each temperature was carried 
out for 300 ps.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 3.A
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Ni}
\label{sec:elementary_Ni}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Ni - EOS
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[htp]
\centering
\includegraphics[scale=0.65]{figures/Ni_all_eos.png}
\caption{\label{fig:Ni_eam_eos} The energy-volume curves of the original EAM, 
SNAP, ML-EAM and DFT for the fcc Ni.}
\end{figure}

We first use the elementary fcc Ni dataset to show our approach. This dataset 
has 461 structures in total. 400 were randomly selected to form the training 
subset. In this experiment, $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and 
$\chi_{\mathrm{elastic}}$ were set to 1, 3 and 0.05 respectively. The batch size
was 25. Only the fcc Ni was included in $\Omega$ (Equation \ref{eq:rose_loss} 
and \ref{eq:cijkl_loss}).

Table \ref{table:elementary_Ni_mae} shows the MAEs of those models. The original 
EAM model already has an accepetable performace on this fcc dataset. Its energy 
MAE is 10.6 meV/atom and the force MAE is 0.06 eV/\AA. The MEAM performs 
slightly worse on this dataset with an energy MAE of 17.6 meV/atom and force MAE
of 0.08 eV/\AA. Our machine learning approach can further reduce the energy MAE 
to 4.1 meV/atom and the force MAE to 0.05 eV/\AA, which are much closer to the 
elementary SNAP Ni model.

Figure \ref{fig:Ni_eam_eos} plots the equation of state curves obtained with the 
DFT, SNAP, EAM and ML-EAM models. The whole fitting region ranges from 84\% to 
118\% of the equilibrium volume. The original EAM significantly underestimates 
the energy at both tensile and compress strains. However, our machine learning 
approach together with the Rose constraint can fix this problem. The 
energy-volume curve of ML-EAM overalps with the DFT curve very well for the 
entire fitting region.

Table \ref{table:elementary_Ni} summerizes the predicted material properties of 
fcc Ni, including the melting point, the elastic constants, the vacancy 
formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
$E_{a}$. The original EAM already performs well on these properties. ML-EAM 
further improves the elastic constants. The errors were significantly reduced 
to around 1-2\%.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Ni - MAE
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\hline
 MAE & SNAP & EAM & MEAM & ML-EAM \\
\hline
Energy (meV/atom) & 1.2 & 10.6 & 17.8 & 4.1 \\
Force (eV/\AA) & 0.05 & 0.06 & 0.08 & 0.05 \\
\hline
\end{tabular}
\caption{\label{table:elementary_Ni_mae} Comparion of the energy and force 
accuracy of the elementary SNAP Ni model, the original EAM, the MEAM and our 
ML-EAM.
}
\end{table}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Ni - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}[htp]
\centering
\begin{tabular}{lcccccc}
\hline
    & DFT & SNAP & EAM & MEAM & ML-EAM & Exp. \\
\hline
$T_{m}$(K) & & 1785 & 1520 & 1765 & 1520 & 1728 \\
$c_{11}$ (GPa) & 276 & 276 (0.0\%) & 248 (-10.1\%) & 260 (-5.8\%) & 274 (-0.7\%) & 261 \\
$c_{12}$ (GPa) & 159 & 159 (0.0\%) & 147 (-7.5\%) & 151 (0.0\%) & 163 (2.5\%) & 151 \\
$c_{44}$ (GPa) & 132 & 132 (0.0\%) & 125 (-5.3\%) & 131 (0.0\%) & 131 (-0.8\%) & 132 \\
$E_{v}$ (eV) & 1.46 & 1.68 (15.1\%) & 1.68 (15.1\%) & 1.16 (-20.5\%) & 1.71 (17.1\%) & 1.54–1.80 \\
$E_{m}$ (eV) & 1.12 & 1.07 (-4.5\%) & 0.90 (-19.6\%) & 1.46 (30.5\%) & 0.87 (-22.3\%) & 1.01–1.48 \\
$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%) & 2.58 (0.0\%) & 2.62 (1.6\%) & 2.58 (0.0\%) & 2.77–2.95 \\
\hline
\end{tabular}
\caption{\label{table:elementary_Ni} Comparison of the calculated and 
experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
formation energy and migration energy, respectively. SNAP refers to the 
elementary Ni SNAP model.
}
\end{table*}

Figure \ref{fig:Ni_eam} compares the $rho(r)$, $F(\rho)$ and $\phi(r)$ functions
of ML-EAM with original Zjw04 EAM. The pairwise potential $\phi(r)$ almost 
remains the same while the embedding function $F(\rho)$ and the electron density 
function $\rho(r)$ changes significantly. Both $\rho(r)$ and $\phi(r)$ converge
to zero at around $r=4.8$ \AA, which is rougly 2 times of the equilibrium 
spacing between nearest neighbors.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Ni - EAM - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure*}[htp]
\centering
\includegraphics[scale=0.57]{figures/Ni_eam.png}
\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
Zjw04 EAM and the machine learned EAM (ML-EAM).}
\end{figure*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 3.B
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Mo}
\label{sec:elementary_Mo}

The second test example is bcc Mo. This dataset has 284 structures. 34 of 
them were used as the testing subset and the rest were used for training. 
The training settings were the same with fcc Ni. An ADP potential was also 
optimized for bcc Mo.

Table \ref{table:elementary_Mo_mae} summerizes the energy and force MAEs on the 
test subset. The original Zjw04 EAM performs significantly worse. The energy

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Mo - EAM/ADP - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure*}[htp]
\centering
\includegraphics[scale=0.6]{figures/Mo_eam_adp.png}
\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
ML-ADP.}
\end{figure*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - MAE
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\hline
 MAE   & SNAP & EAM & ML-EAM & ML-ADP \\
\hline
Energy (meV/atom) & 13.2 & 58.9 & 21.7 & 22.8 \\
Force (eV/\AA) & 0.25 & 0.31 & 0.28 & 0.27 \\
\hline
\end{tabular}
\caption{\label{table:elementary_Mo_mae} Comparion of the energy and force 
accuracy of the elementary SNAP Ni model, the original EAM, the MEAM and our 
ML-EAM.
}
\end{table}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}[htp]
\centering
\begin{tabular}{lcccccc}
\hline
    & DFT & SNAP & EAM & ML-EAM & ML-ADP & Exp. \\
\hline
$T_{m}$(K) & & 3000 & 3750 & 2940 & 2880 & 2890 \\
$c_{11}$ (GPa) & 472 & 473 (0.2\%) & 456 (-3.4\%) & 260 (-5.8\%) & 274 (-0.7\%) & 479 \\
$c_{12}$ (GPa) & 158 & 152 (-3.8\%) & 167 (5.7\%) & 151 (0.0\%) & 163 (2.5\%) & 165 \\
$c_{44}$ (GPa) & 106 & 107 (0.9\%) & 115 (8.5\%) & 131 (0.0\%) & 131 (-0.8\%) & 108 \\
$E_{v}$ (eV) & 2.87 & 2.61 (-9.1\%) & 3.02 (5.2\%) & 1.16 (-20.5\%) & 1.71 (17.1\%) & \\
$E_{m}$ (eV) & 1.12 & 1.39 (24.1\%) & 1.54 (37.5\%) & 1.46 (30.5\%) & 0.87 (-22.3\%) & \\
$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%) & 4.56 (14.3\%) & 2.62 (1.6\%) & 2.58 (0.0\%) & 4.00 \\
\hline
\end{tabular}
\caption{\label{table:elementary_Mo} Comparison of the calculated and 
experimental material properties of elementary bcc Mo. SNAP refers to the 
elementary Mo SNAP model.
}
\end{table*}

@@

\begin{table*}[h]
\centering
\begin{tabular}{lcccccccc}
\hline
                  & Model  & Mo   & Ni$_4$Mo & Ni$_3$Mo & Mo$_{\mathrm{Ni}}$ & Ni$_{\mathrm{Mo}}$ & Ni   & Overall \\
\hline
Energy (meV/atom) & SNAP   & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
                  & EAM    & 58.9 & 211.2    & 255.6    & 46.5               & 147.6              & 10.6 & 117.2   \\
                  & ML-EAM & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
                  & ML-ADP & 36.9 & 5.1      & 4.8      & 21.7               & 22.8               & 13.3 & 19.6    \\
\hline
Force (eV/\AA)    & SNAP   & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
                  & EAM    & 0.40 & 0.20     & 0.19     & 0.21               & 0.57               & 0.06 & 0.26    \\
                  & ML-EAM & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
                  & ML-ADP & 0.45 & 0.16     & 0.15     & 0.14               & 0.35               & 0.08 & 0.20    \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to the DFT on the entire Mo-Ni dataset.}
\end{table*}

\begin{table*}[h]
\centering
\begin{tabular}{lccccc}
\hline
                   & DFT  & SNAP          & EAM           & ML-EAM        & ML-ADP        \\
\hline
Ni$_3$Mo \\
$c_{11}$           & 385  & 420 (9.1\%)   & 195 (-49.4\%) & 403 (4.7\%)   & 374 (-2.9\%)  \\
$c_{12}$           & 166  & 197 (18.7\%)  & 98 (-41.0\%)  & 208 (25.3\%)  & 160 (-3.6\%)  \\
$c_{13}$           & 145  & 162 (11.7\%)  & 98 (-32.4\%)  & 230 (58.6\%)  & 176 (21.4\%)  \\
$c_{22}$           & 402  & 360 (10.7\%)  & 351 (-12.7\%) & 443 (10.2\%)  & 386 (-4.0\%)  \\
$c_{23}$           & 131  & 145 (-10.4\%) & 107 (13.7\%)  & 272 (107.6\%) & 214 (63.3\%)  \\
$c_{33}$           & 402  & 408 (-10.4\%) & 295 (13.7\%)  & 474 (17.9\%)  & 398 (-0.5\%)  \\
$c_{44}$           & 94   & 84 (-10.4\%)  & 36 (13.7\%)   & 25 (-73.4\%)  & 52 (-44.6\%)  \\
$B_{\mathrm{VRH}}$ & 230  & 243 (5.7\%)   & 156 (-32.2\%) & 302 (31.3\%)  & 250 (8.7\%)   \\
$G_{\mathrm{VRH}}$ & 89   & 100 (12.4\%)  & 61 (-31.5\%)  & 57 (36.0\%)   & 66 (25.8\%)   \\
$\mu$              & 0.33 & 0.32 (-3.0\%) & 0.33 (0.0\%)  & 0.41 (24.2\%) & 0.38 (15.1\%) \\
\hline
Ni$_4$Mo \\
$c_{11}$           & 300  & 283 (-5.7\%)  & 172 (-42.7\%) & 282 (-6.0\%)  & 342 (14.0\%)  \\
$c_{12}$           & 186  & 179 (-3.8\%)  & 158 (-15.1\%) & 125 (-32.8\%) & 217 (16.7\%)  \\
$c_{22}$           & 313  & 326 (4.2\%)   & 158 (-49.5\%) & 282 (-10.0\%) & 342 (9.3\%)   \\
$c_{23}$           & 166  & 164 (-1.2\%)  & 80 (-51.8\%)  & 156 (-6.0\%)  & 232 (39.8\%)  \\
$c_{44}$           & 130  & 126 (-3.1\%)  & 125 (-3.8\%)  & 136 (4.6\%)   & 117 (-10.0\%) \\
$B_{\mathrm{VRH}}$ & 223  & 220 (-1.3\%)  & 161 (-27.8\%) & 178 (-20.1\%) & 257 (15.2\%)  \\
$G_{\mathrm{VRH}}$ & 91   & 95 (4.4\%)    & -156 (-162\%) & 80 (-12.1\%)  & 79 (-13.2\%)  \\
$\mu$              & 0.33 & 0.31 (-6.1\%) & 0.70 (112\%)  & 0.31 (-6.1\%) & 0.36 (9.1\%)  \\
\hline
\end{tabular}
\caption{\label{table:NiMo_elastic_constants}
Comparion of elastic constants ($c_{ij}$, GPa), Voigt-Reuss-Hill bulk modulus 
($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, fcc Mo and binary 
alloys Ni$_{3}$Mo and Ni$_{4}$Mo.
}
\end{table*}

>>>>

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Ni - EAM - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure*}
\centering
\includegraphics[scale=0.57]{figures/Ni_eam.png}
\caption{\label{fig:Ni_eam} $\rho(r)$, $F(\rho)$ and $\phi(r)$ of the original 
Zjw04 EAM and the machine learned EAM (ML-EAM).}
\end{figure*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Ni - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lccccc}
\hline
                              & DFT  & SNAP          & EAM            & ML-EAM         & Exp.      \\
\hline
$T_{m}$(K)                    &      & 1785          & 1520           & 1520           & 1728      \\
$c_{11}$ (GPa)                & 276  & 276 (0.0\%)   & 248 (-10.1\%)  & 274 (-0.7\%)   & 261       \\
$c_{12}$ (GPa)                & 159  & 159 (0.0\%)   & 147 (-7.5\%)   & 163 (2.5\%)    & 151       \\
$c_{44}$ (GPa)                & 132  & 132 (0.0\%)   & 125 (-5.3\%)   & 131 (-0.8\%)   & 132       \\
$B_{\mathrm{VRH}}$ (GPa)      & 198  & 198 (0.0\%)   & 181 (-8.6\%)   & 195 (0.0\%)    & 188       \\
$G_{\mathrm{VRH}}$ (GPa)      & 95   & 95 (0.0\%)    & 87 (-8.4\%)    & 93 (-2.1\%)    & 93        \\
$\mu$                         & 0.29 & 0.29 (0.0\%)  & 0.29 (0.0\%)   & 0.29 (0.0\%)   & 0.29      \\
$E_{v}$ (eV)                  & 1.46 & 1.68 (15.1\%) & 1.68 (15.1\%)  & 1.71 (17.1\%)  & 1.54–1.80 \\
$E_{m}$ (eV)                  & 1.12 & 1.07 (-4.5\%) & 0.90 (-19.6\%) & 0.87 (-22.3\%) & 1.01–1.48 \\
$E_{a} = E_{v} + E_{m} $ (eV) & 2.58 & 2.75 (6.6\%)  & 2.58 (0.0\%)   & 2.58 (0.0\%)   & 2.77–2.95 \\
\hline
\end{tabular}
\caption{\label{table:Ni_properties} Comparison of the calculated and 
experimental material properties of elementary fcc Ni. $T_{m}$ is the melting 
point. $c_{ij}$ represents elastic constants. $E_{v}$ and $E_{m}$ are vacancy 
formation energy and migration energy, respectively. SNAP refers to the 
elementary Ni SNAP model.
}
\end{table*}

@@

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Section 3.A
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Elementary Ni and Mo}
\label{sec:elementary}

We first use the two elementary datasets (Ni and Mo) to show our approach. These 
two datasets has 461 and 284 structures, respectively. 61 and 34 were randomly 
selected to form the test subsets. In these two experiments, 
$\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ and $\chi_{\mathrm{elastic}}$ were 
set to 1, 3 and 0.05 respectively. The batch size was fixed to 25.

The original Zjw04 potentials were fitted to experimentally obtained quantities.
Thus, we use the relative MAE:
\begin{equation}
\mathbf{rMAE} = \frac{1}{N}\sum_{i=1}^{N}{
    | \frac{(E_i - E_i^{dft})}{N_i} - (E_{eq} - E_{eq}^{dft}) |
}
\end{equation}
to measure their performaces. Here $N_i$ is the number of atoms in structure 
$i$, $E_i$ is the Zjw04 energy of structure $i$ while $E_i^{dft}$ represents its 
corresponding DFT energy, $E_{eq}$ and $E_{eq}^{dft}$ refers to the equilibrium 
energy of Zjw04 and DFT, respectively.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: r(Mo-Mo)
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}
\centering
\includegraphics[scale=0.64]{figures/r_MoMo_hist.png}
\caption{\label{fig:r_MoMo_hist} The energy-volume curves of the original EAM, 
SNAP, ML-EAM and DFT for the fcc Ni.}
\end{figure}

Figure \ref{fig:Mo_eam_adp} compares the $\rho(r)$, $F(\rho)$, $\phi(r)$, 
$\mu(r)$ and $\omega(r)$ functions. The differences between ML-EAM and ML-ADP 
$\rho(r)$, $\phi(r)$ and $F(\rho)$ are quite small. Both the angular-dependent 
dipole $\mu(r)$ and quadrupole $\omega(r)$ quickly descrease to zero at 2.5 \AA. 
However, the equilibrium spacing between two adjacent Mo atoms is 2.7 \AA. This 
may explain why ML-ADP does not outperform ML-EAM on this dataset: most 
$r^{\mathrm{Mo-Mo}}$ are beyond 2.5 \AA (Figure \ref{fig:r_MoMo_hist}).

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Ni - EOS
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}
\centering
\includegraphics[scale=0.65]{figures/Ni_all_eos.png}
\caption{\label{fig:Ni_eos} The energy-volume curves of the original EAM, 
ML-EAM and DFT for the fcc Ni.}
\end{figure}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Mo - EOS
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}
\centering
\includegraphics[scale=0.65]{figures/Mo_all_eos.png}
\caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
ML-EAM and DFT for the fcc Ni.}
\end{figure}

For the Ni dataset, the original Zjw04 already has a reasonable performace. 
The energy \textbf{rMAE} is 10.6 meV/atom and the force MAE is just 0.06 eV/\AA 
on the entire dataset. Our machine learning approach can further enhance the 
performace. ML-EAM achieves 4.1 meV/atom and 0.05 eV/\AA on the test set and 
3.9 meV/atom and 0.05 eV\AA on the entire dataset. ML-EAM is nearly as accurate 
as SNAP (1.2 meV/atom, 0.05 eV\AA), but later has around three orders of 
magnitude more computational expense. Figure \ref{fig:Ni_eam} demonstrates the 
$\rho(r)$, $F(\rho)$ and $\phi(r)$ functions before (Zjw04) and after machine 
learning optimization. The pairwise potential $\phi(r)$ almost remains the same 
while the embedding function $F(\rho)$ and the electron density function 
$\rho(r)$ changes significantly. Both $\rho(r)$ and $\phi(r)$ converge to zero 
at around $r=4.8$ \AA, which is rougly 2 times of the equilibrium spacing 
between nearest neighbors.

For the Mo dataset, the situation is quite different. The original Zjw04 has 
extremely large MAEs: the energy \textbf{rMAE} is $\sim 98$ meV/atom and the 
force MAE is more than 0.40 eV/\AA. Our method can significantly reduce the 
error: ML-EAM can achieve test MAEs of 21.9 meV/atom and 0.28 eV/\AA and overall
MAEs of 28.1 meV/atom and 0.32 eV/\AA. We also optimized an ADP potential for 
this dataset. Interestingly, ML-ADP achieves almost exactly the same MAEs with 
ML-EAM: 22.1 meV/atom and 0.27 eV\AA on the test set and 27.9 meV/atom and 0.33 
eV/\AA on the entire dataset. On the contrast, the SNAP method (13.2 meV/atom, 
0.25 eV/\AA) behaves better. But considering the computational cost, the 
optimized EAM and ADP are totally accepetable.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccc}
\hline
                              & DFT  & SNAP          & EAM           & ML-EAM         & ML-ADP         & Exp. \\
\hline
$T_{m}$(K)                    &      & 3000          & 3750          & 2940           & 2880           & 2890 \\
$c_{11}$ (GPa)                & 472  & 473 (0.2\%)   & 457 (-3.2\%)  & 472 (0.0\%)    & 473 (0.2\%)    & 479  \\
$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)  & 168 (6.3\%)   & 158 (0.0\%)    & 160 (1.2\%)    & 165  \\
$c_{44}$ (GPa)                & 106  & 107 (0.9\%)   & 116 (9.4\%)   & 106 (0.0\%)    & 105 (-0.9\%)   & 108  \\
$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)  & 264 (0.4\%)   & 262 (-0.4\%)   & 264 (0.4\%)    & 270  \\
$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)   & 127 (2.4\%)   & 125 (0.8\%)    & 124 (0.0\%)    & 125  \\
$\mu$                         & 0.30 & 0.29 (-3.3\%) & 0.29 (-3.3\%) & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30 \\
$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%) & 3.02 (5.2\%)  & 1.16 (-20.5\%) & 1.71 (17.1\%)  &      \\
$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%) & 1.54 (37.5\%) & 1.46 (30.5\%)  & 0.87 (-22.3\%) &      \\
$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%) & 4.56 (14.3\%) & 2.62 (1.6\%)   & 2.58 (0.0\%)   & 4.00 \\
\hline
\end{tabular}
\caption{\label{table:Mo_properties} Comparison of the calculated and 
experimental material properties of elementary bcc Mo. SNAP refers to the 
elementary Mo SNAP model.
}
\end{table*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Alloy EOS - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure*}
\centering
\includegraphics[scale=0.5]{figures/alloy_eos.png}
\caption{\label{fig:alloy_eos} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
ML-ADP.}
\end{figure*}

Figure \ref{fig:Ni_eos} and \ref{fig:Mo_eos} plot the equation of state 
curves. The fitting region ranges from 84\% to 118\% of the corresponding 
equilibrium volume. For both crystals, the original EAM significantly 
underestimate the energy at both tensile and compress strains. However, our 
constrained machine learning approach can fix this problem. The 
energy-volume curves of ML-EAM and ML-ADP overalp with the DFT curves very well.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Mo - EAM/ADP - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}[htp]
\centering
\includegraphics[scale=0.6]{figures/Mo_eam_adp.png}
\caption{\label{fig:Mo_eam_adp} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
ML-ADP.}
\end{figure}

Table \ref{table:Ni_properties} and \ref{table:Mo_properties} summerize the 
predicted material properties of fcc Ni and bcc Mo, including the melting point 
$T_{m}$, the elastic constants ($c_{11}$, $c_{12}$ and $c_{44}$), the vacancy 
formation energy $E_{v}$, the migration energy $E_{m}$ and the activation energy 
$E_{a}$. The original Zjw04 potentials were developed by fitting material 
properties so they already perform well on these metrics. Our ML-EAM and ML-ADP 
not only inherit this feature but also gain significant improvement on 
predicting elastic constants: the relative errors of the elastic constants as 
well as the Voigt-Reuss-Hill bulk modulus, shear modulus and homogeneous 
Poisson's ratio, for both bcc Mo and fcc Ni, are reduced from $\sim$10\% to 
0-2\%.

We further examined our ML-EAM and ML-ADP by calculating the melting temperature
of fcc Ni and bcc Mo using the solid-liquid coexistence approach. For fcc Ni, 
$30 \times 10 \times 10$ supercells were used and for bcc the supercells were 
$30 \times 15 \times 15$. The time step was set to 1 fs. The simulation for each 
temperature was carried out for at least 300 ps. For fcc Ni, $T_{m}$ remains the 
same for ML-EAM, 200 K lower than the experiment $T_m$. However, the calculated 
$T_{m}$ of Mo is greatly improved. The original Zjw04 $T_{m}$ is around 3750 K, 
800 K higher than experiment (2890 K). Both ML-EAM and ML-ADP can give very 
accurate melting temperature.

@@

Secondly, we tested our method on the entire binary Mo-Ni dataset. 300 
structures were randomly splitted to form the test dataset and the rest 3673 
were used to train the potentials. $\chi_{\mathrm{f}}$, $\chi_{\mathrm{rose}}$ 
and $\chi_{\mathrm{elastic}}$ were set to 1, 1 and 0.05 respectively. The batch 
size was increased to 50. Only the equilibrium fcc Ni and bcc Mo are included in 
$\Omega$ of Equation \ref{eq:cijkl_loss} and \ref{eq:rose_loss}.

The original EAM uses a simplified interpolation form to describe the pairwise 
interaction of A-B (Equation \ref{eq:zjw04_phi_ab}). However, we did a minor 
modification: by adding more fitting parameters we use Equation 
\ref{eq:zjw04_phi_aa} directly. Thus, in total, there are 44 learnable 
parameters for ML-EAM and 68 for ML-ADP. One should note that in this section, 
SNAP, ML-EAM and ML-ADP all refer to their corresponding binary form.

Table \ref{table:MAE} summarizes the energy and force MAEs of SNAP, ML-EAM and 
ML-ADP on the different subsets. Amazingly, ML-ADP becomes the overally best. 
Both the energy MAE (19.6 meV/atom) and the force MAE (0.20 eV/\AA) are smaller 
than those of the binary SNAP (22.5 meV/atom and 0.23 eV/\AA). 
The pure Mo is still a challenge for ML-ADP as the energy and force MAEs are 
noticeably large (still much smaller than the original Zjw04 EAM). The binary 
SNAP predicts well on pure Ni and Mo. But ML-ADP outperforms the SNAP model on 
binary phases (Ni$_3$Mo, Ni-doped Mo and especially the Mo-doped Ni).
On the contrast, ML-EAM performs significantly worse compared with ML-ADP. 
Interestingly, our results suggest that Mo-Ni dipole and quadrupole interactions 
are completely negligible (Figure S1 in the appendix). The Ni-Ni dipole and 
quadrupole interactions are an order of magnitude weaken than those of Mo-Mo.

Figure \ref{fig:alloy_eos} demonstrates the energy-volume curves of Ni$_3$Mo and
Ni$_4$Mo. The original Zjw04 EAM can not properly describe the energy-volume 
relations of these two crystals. The ML-ADP curves fit perfectly with the DFT 
curves. ML-EAM fits well with tensile strains but overestimates the energy under 
compress strains.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo-Ni MAE
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccccc}
\hline
                  & Model  & Mo   & Ni$_4$Mo & Ni$_3$Mo & Mo$_{\mathrm{Ni}}$ & Ni$_{\mathrm{Mo}}$ & Ni   & Overall \\
\hline
Energy (meV/atom) & SNAP   & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
                  & ML-EAM & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
                  & ML-ADP & 36.9 & 5.1      & 4.8      & 21.7               & 22.8               & 13.3 & 19.6    \\
\hline
Force (eV/\AA)    & SNAP   & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
                  & ML-EAM & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
                  & ML-ADP & 0.45 & 0.16     & 0.15     & 0.14               & 0.35               & 0.08 & 0.20    \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to the DFT on the entire Mo-Ni dataset.}
\end{table*}

Table \ref{table:NiMo_elastic_constants} summarizes the elastic constants 
predictions of Ni$_3$Mo and Ni$_4$Mo. One should note that these two crystals 
were not included in $\Omega$ of Equation \ref{eq:cijkl_loss} and 
\ref{eq:rose_loss} but their elastic properties were used to tune the binary 
SNAP model. The original Zjw04 EAM performs obviously poorly on predicting 
elastic constants. Some absolute percentage errors can even exceed 100\%. With 
our machine learning correction, ML-EAM, especially ML-ADP, can give much more  
accurate predictions. For the Ni$_3$Mo crystal, the average absolute percentage 
error is reduced from 40\% (Zjw04) to 20\% (ML-ADP). ML-ADP even beats SNAP on 4 
($c_{11}$, $c_{12}$, $c_{22}$ and $c_{3}$) of the 7 elastic metrics. For the 
Ni$_4$Mo crystal, the average absolute percentage error is also descreased.
